\documentclass[letterpaper,10pt,titlepage]{IEEEtran}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}

\def\name{Alessandro Lim, Kevin Turkington}
\author{\name}
\title{CS 444 Assignment 4}

%pull in the necessary preamble matter for pygments output
%\input{pygments.tex}

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {cs444 ``operating systems 2'' assignment 4},
  pdftitle = {CS 444 Assignment 4},
  pdfpagemode = UseNone
}

\begin{document}
\maketitle
\hrulefill

\section{Assignment4 Questions}
\subsection{What do you think the main point of this assignment is?}
The main point of this assignment was to familiarize our selfs with the kernel, and gain the ability to find resources to aid with testing. And familiarizing our selfs with different algorithms and the various ways they can be implemented into the kernel.

\subsection{How did you personally approach the problem? Design decisions, algorithm, etc.} 
First we found pseudo code for the best fit algorithm, and tried to match our kernel implementation as closely as possible to the found algorithm.

\subsection{How did you ensure your solution was correct? Testing details, for instance.} 
We knew our implementation was correct when the kernel didn't hang on boot forever, after several attempt creating the best fit slob. The we created a system call to get fragmentation rates of the disk, and on average the best fit algorithm did better than first fit.

\subsection{What did you learn?}
forgetting a single line of code can lead to alot of headaches. and there are many ways to verify if an implementation is running, its just a matter of finding which way works best.

\begin{table*}
\section{Work Log}
\input{worklog.tex}
\end{table*}

\begin{table*}
\section{Gitlog}
\input{gitlog.tex}
\end{table*}

    
% bibliography
\nocite{*}%if nothing is referenced it will still show up in refs
\bibliographystyle{plain}
\bibliography{refs}
%end bibliography

%input the pygmentized output of mt19937ar.c, using a (hopefully) unique name
%this file only exists at compile time. Feel free to change that.
\end{document}
